Notebook of learning from ensemble labels

### 2021-07-03 docs/notebook_learn_dl_ensemble.Rmd
Make some changes

>>>>

#### Prediction

```
python hrlcm/predict.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/final.pth' --fname_predict 'results/north/dl_catalog_valid_full.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
```
